Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1) \note{\scriptsize Authors, please add/check middle initials and affiliations}

### 2014-04-11 WSSSPE1_report/WSSSPE1_summary_report.tex
Author details for James H; tidied up double citation; fixed cite re environmental sustainability

\thanks{{}$^{(1)}$ National Science Foundation, Arlington, VA, USA; Computation Institute, University of Chicago \& Argonne National Laboratory, Chicago, IL, USA; \url{d.katz@ieee.org}}
%
\thanks{{}$^{(2)}$ National Evolutionary Synthesis Center (NESCent),
  Durham, NC, USA; \url{hlapp@nescent.org}}
%
\thanks{{}$^{(3)}$ Argonne National Laboratory, Chicago, IL, USA; \url{ketan@anl.gov}}
%
\thanks{{}$^{(4)}$ Center for Computation and Technology, Louisiana State University, Baton Rouge, LA, USA; \url{knarf@cct.lsu.edu}}
%
\thanks{{}$^{(5)}$ Columbia Astrophysics Laboratory, Columbia University, New
York, NY, USA; \url{matthewturk@gmail.com}}
%
\thanks{{}$^{(7)}$ San Diego Supercomputer Center, University of California San Diego, La Jolla, CA, USA, \url{wilkinsn@sdsc.edu}}
%
\thanks{{}$^{(8)}$ Leader, Research Software Development Team, University College London; \url {j.hetherington@ucl.ac.uk}}
%
\thanks{{}$^{(9)}$ xxx}
%
\thanks{{}$^{(10)}$ NORC at the University of Chicago and the Illinois Institute of Technology, Chicago, IL, USA; \url{sctchoi@uchicago.edu}}
% 
\thanks{{}$^{(11)}$ xxx}
%
\thanks{{}$^{(12)}$ xxx}
%
\thanks{{}$^{(13)}$ xxx}
%
\thanks{{}$^{(14)}$ xxx}

@@

One area in which there was not complete overlap was whether the word
(and thus the effort called for by the WSSSPE workshop) involved
environmental sustainability. Of course the word sustainability has
strong connotations from consideration of environmental issues,
evoking some mention of the areas in which software interacts with
overall environmental resource usage, particularly energy efficiency.
The two papers in this area which mentioned this\todo{which are these
  papers? Should cite here.} did so without
integrating that analysis into the question of software being around
long-term, suggesting that questions of environmental impact of
scientific software is a conceptually distinct area of inquiry.

@@

The literature below, suggested by attendees, addresses both non-scientific
software projects, as well as scientific projects.  The selections address both
descriptive and prescriptive approaches to communities. 
\begin{itemize}
\item \cite{howison_scientific_2011}
\item \cite{citeulike:11831265}
\item \cite{citeulike:7888211}
\item \cite{citeulike:478633}
\item \cite{opac-b1134063}
\item \cite{DBLP:conf/cscw/HowisonH11}
\item \cite{DBLP:conf/cscw/2011}
\item \cite{Trapani:2011}
\item \cite{Allsopp:2012}
\item \cite{1749-4699-6-1-015010}
\item \cite{Turk:2013:SCH:2484762.2484782}
\end{itemize}

>>>>

\thanks{{}$^{(1)}$ National Science Foundation, Arlington, VA, USA; Computation Institute, University of Chicago \& Argonne National Laboratory, Chicago, IL, USA; \url{d.katz@ieee.org}}
%
\thanks{{}$^{(2)}$ National Evolutionary Synthesis Center (NESCent),
  Durham, NC, USA; \url{hlapp@nescent.org}}
%
\thanks{{}$^{(3)}$ Argonne National Laboratory, Chicago, IL, USA; \url{ketan@anl.gov}}
%
\thanks{{}$^{(4)}$ Center for Computation and Technology, Louisiana State University, Baton Rouge, LA, USA; \url{knarf@cct.lsu.edu}}
%
\thanks{{}$^{(5)}$ Columbia Astrophysics Laboratory, Columbia University, New
York, NY, USA; \url{matthewturk@gmail.com}}
%
\thanks{{}$^{(7)}$ San Diego Supercomputer Center, University of California San Diego, La Jolla, CA, USA, \url{wilkinsn@sdsc.edu}}
%
\thanks{{}$^{(8)}$ Leader, Research Software Development Team, University College London; \url {j.hetherington@ucl.ac.uk}}
%
\thanks{{}$^{(9)}$ University of Texas at Austin; jhowison@ischool.utexas.edu}
%
\thanks{{}$^{(10)}$ NORC at the University of Chicago and the Illinois Institute of Technology, Chicago, IL, USA; \url{sctchoi@uchicago.edu}}
% 
\thanks{{}$^{(11)}$ xxx}
%
\thanks{{}$^{(12)}$ xxx}
%
\thanks{{}$^{(13)}$ xxx}
%
\thanks{{}$^{(14)}$ xxx}

@@

One area in which there was not complete overlap was whether the word
(and thus the effort called for by the WSSSPE workshop) involved
environmental sustainability. Of course the word sustainability has
strong connotations from consideration of environmental issues,
evoking some mention of the areas in which software interacts with
overall environmental resource usage, particularly energy efficiency.
The two papers in this area which mentioned this~\cite{Venters_WSSSPE,Calero_WSSSPE} did so without
integrating that analysis into the question of software being around
long-term, suggesting that questions of environmental impact of
scientific software is a conceptually distinct area of inquiry.

@@

The literature below, suggested by attendees, addresses both non-scientific
software projects, as well as scientific projects.  The selections address both
descriptive and prescriptive approaches to communities. 
\begin{itemize}
\item \cite{howison_scientific_2011, howison_incentives_2013}
\item \cite{citeulike:11831265}
\item \cite{citeulike:7888211}
\item \cite{citeulike:478633}
\item \cite{opac-b1134063}
\item \cite{Trapani:2011}
\item \cite{Allsopp:2012}
\item \cite{1749-4699-6-1-015010}
\item \cite{Turk:2013:SCH:2484762.2484782}
\end{itemize}
